An IFS study of Low-powered Radio Galaxies

### 2019-12-30 paper.tex
Further work
 Changes to be committed:
	modified:   paper.tex

In general, our Southern Sample galaxies show old, metal-rich and
alpha-enhanced SSPs, characteristics that are common in ETGs {\bf (Add
  a classic reference here.)} The exceptions are NGC~612 and
NGC~1316. NGC~1316 has a very young stellar population (our fit of
$t\approx2$~Gyr is consistent with that of \citealt{Kuntschner2000},
but is conflicting with the older and less metal-rich estimate of
\citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
$\mathrm{[Fe/H]}=0.12\pm0.01$ for an aperture covering the central
$0.1$~kpc). {\bf (Is that a circular or square aperture? If circular,
  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
to have an extended young stellar population of
$t\approx4$~Gyr. Otherwise, NGC~3557 is notable for containing a
significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr)
along the south-east branch of the molecular gas (white contours in
Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
  to in the NGC3100 maps, and the CO is distributed North-East to
  South-West, so there is no South-East CO ``branch''. Perhaps you
  meant South-West (where there is indeed a blue region in the
  H$\beta$ map, if not in the age map)? Also, there is no white
  contour in the figure. The CO contours are in pale
  blue/turquoise. Is that what you meant? In any case, this needs to
  be corrected to reflect the truth.)}

@@

\added{\citet{McDermid2006}} \removed{\citet{Kuntschner2010}} showed that 
KDCs can be separated into two classes: either small with various stellar 
ages or typically larger but containing a homogeneously old stellar 
population. {\bf (I thought the first to point this out was 
McDermid et al.\ (2006; see e.g.\ their Fig.~16), which should at 
least also be quoted here. Check and possibly correct.)} 
\added{Using the method of \ctiet{McDermid2006},} the size 
\added{and age} of the KDC is defined as the radius
where the superposition of the two kinematic components (the KDC and
the host galaxy) results in a local minimum in the mean velocity \added{and} the
age of the most-likely SSP model for the spatially integrated spectrum
within a central \added{, circular} aperture with a \added{radius} of 
$1\arcsec$ {\bf (Again, square or circular, radius or diameter? Clarify.)} 
\removed{is taken as the KDC's age.} \added{, repectively.} 
{\bf (Are these two definitions (of the KDCs' sizes and ages) 
those of \citealt{Kuntschner2010} or yours or both? Clarify.)}

@@

\textbf{NGC~3100} has an interesting ISM morphology. The
\ce{^{12}CO(2-1)} integrated intensity contours (overlaid on the IFS
maps in white; see Fig.~\ref{fig:ngc3100}) {\bf (Again, no white
  contours in the figure... pale blue/turquoise contours?)} show a
broken ring, the radio jet passing through the gaps, hence suggesting
a jet-ring interaction \citep[see][]{ruffa2019, ruffa2020}. The
ionised gas is brightest in those same gaps, that we interpret as
additional excitation of the gas due to shocks from the impact of the
jet. It is unclear if the ionised gas kinematics supports this
interpretation, being completely different than that of the stars (and
nearly totally blueshifted). The centre of rotation of the gas also
appears to be offset from the centre of the galaxy (as defined by its
stellar surface brightness), by several arcseconds to the west. {\bf
  (I really do not understand how you can identify a centre of
  rotation when there is no evidence of organised rotation at
  all. Either convince me of that or remove/change that
  comment. Perhaps mention the lack of obvious large-scale rotation
  instead?!)}

@@

To check if the LINER classifications are due to central radiation
sources (such as AGN) or extended sources (such as weak star formation
or stars on the post-asymptotic giant branch, pAGB), {\bf (What about
  extended horizontal branch stars (again below)? Mention/discuss.)}
we examine the H$\alpha$ and H$\beta$ flux radial profiles of our
Southern Sample galaxies with extended detected ionised gas (see
Section~\ref{subsubsec:Hb}). Finally, we use the mass\,--\,excitation
(MEx) plot of \cite{Nyland2016}, using parameters derived from spectra
spatially-integrated over central circular apertures of radius
$3\arcsec$, thus probing only the central regions of the galaxies (see
Section~\ref{subsubsec:MEx}). {\bf (You talked here of *the*
  spatially-integrated spectra, as if spectra within a central
  $3\arcsec$ aperture had been used before, but this is not the case
  (only $2\arcsec$ and $1\arcsec$ apertures were used for stellar
  populations). Are these new or previously-generated spectra?
  Clarify.)} This allows us to classify the remaining galaxies (with
no spatially-extended ionised gas) into the star-forming, Seyfert~2,
LINER, transition or passive class, and to subdivide LINER galaxies
into those whose LINER characteristics are attributable to a central
AGN (labelled as LINER-AGN) and those whose LINER characteristics are
not. {\bf (Labelled as what? LIER?  Clarify.)} As the least
conventional, we expand on the final two steps in the two sub-sections
below, while the final classifications are listed in~Table
\ref{tab:derivedProp}.

@@

In Section~\ref{sec:StarKine}, we showed that in terms of their
stellar kinematic properties our radio-selected Southern Sample
galaxies are no different than ordinary optically-selected ETGs, i.e.\
our sample shows a mixture of regularly- and non-regularly-rotating
objects. Both classes also appear consistent with observations of the
intrinsic shapes of ordinary regular and non-regular rotators. {\bf (I
  do not actually know/understand what you were trying to say or refer
  to in the last sentence. Are you referring to the misalignment angle
  $\Gamma_\text{kin}$ of regular and non-regular rotators? What do you
  mean by ``observations of the intrinsic shapes''? Clarify.)} We
established that two (tentatively three) galaxies host a large KDC. We
also classified our sample galaxies into fast- and slow-rotators and,
once differences in the mass distributions of our Southern Sample and
the A+M sample were taken into account, we found a fraction of
slow-rotators ($45\pm13\%$) consistent with that of ordinary ETGs.

@@

In Section~\ref{sec:gas}, we showed that our Southern Sample galaxies
have ionised gas masses of $10^4$\,--\,$10^6$~$\mathrm{M_\odot}$. As
our sample contains particularly massive galaxies, high ionised gas
masses are not unexpected, but these masses are at the upper limit of,
and possibly exceed {\bf (Again, why ``possibly''? They either always
  exceed, generally exceed, occasionally exceed, or never exceed!
  Check and clarify.)}, the typical masses observed in ETGs,

@@

JW acknowledges funding from the Science and Technology Facilities
Council Grant Code 1577871. This research made extensive use of
observation from VIMOS \citep{LeFevre2003} and archival data from MUSE
\citep{Bacon2010}. We also made use of observations from APEX
\citep{Gusten2006} and ALMA. ALMA is a partnership of ESO
(representing its member states), the National Science Foundation
(NSF; USA) and the National Institutes of Natural Sciences (NINS;
Japan), together with the National Research Council (NRC; Canada), the
Ministry of Science and Technology (MOST; Taiwan) and Academia Sinica
Institute of Astronomy and Astrophysics (ASIAA; Taiwan), and Korea
Astronomy and Space Science Institute (KASI; Republic of Korea), in
cooperation with the Republic of Chile. The Joint ALMA Observatory is
operated by ESO, Associated Universities Inc./National Radio Astronomy
Observatory (AUI/NRAO; USA) and National Astronomical Observatory of
Japan (NAOJ). We also made use of data products from 2MASS, which is a
joint project of the University of Massachusetts and the Infrared
Processing and Analysis Center (IPAC)/California Institute of
Technology, funded by the National Aeronautics and Space
Administration (NASA) and NSF. We also made use of the Set of
Identifications, Measurements and Bibliography for astronomical Data
(SIMBAD) database and portal tool, operated at the Strasbourg
astronomical Data Centre (CDS), France. This research has made use of
the following resources and programs: arXiv.org; the Astrophysics Data
System (ADS); \textsc{astropy}, a community-developed core
\textsc{python} package for astronomy
\citep{TheAstropyCollaboration2013}; \textsc{kinemetry}
\citep{Krajnovic2006}; \textsc{ipython} \citep{Perez2007};
\textsc{matplotlib} \citep{Hunter2007}; \textsc{p3d}
\citep{Sandin2010, Sandin2011}; \textsc{pPXF} \citep{Cappellari2004};
\textsc{py3d} \citep{Sanchez2011, Husemann2013, Husemann2014};
\textsc{scipy} \citep{Oliphant2007, Millman2011}; \textsc{numpy}
\citep{VanderWalt2011}; \textsc{spectools} (Ryan Houghton and Simon
Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning}
\citep[including the SAURON colourmaps {\bf (Colourmaps, whatever that
  might be, or colour table? Clarify.)}; ][]{Cappellari2003}.

@@

\begin{figure*}
  \centering
  % \includegraphics[width=\textwidth]{eso443-g024.png}
  \caption{Spatially-resolved map of all the parameters derived from
    the VIMOS observations of ESO~443-G24. Each parameter is indicated
    in the top-left corner of each panel, and the colour scale limits
    are listed in the bottom-right corner of each panel. {\bf (Why are
      these not perfect fits to the bottom-right corners? Fix?)} The
    surface brightness (isophotes) are overlaid as black contours in
    all the maps, while the \ce{^{12}CO(2-1)} contours from ALMA are
    overlaid in white {\bf (Pale blue or turquoise? Correct.)} and the
    radio continuum contours from the VLA are overlaid in green. The
    radio band displayed depends on the data and angular resolution
    available \citep[see][]{ruffa2019, ruffa2020}. {\bf
      (``Metalicity'' should be ``Metallicity''. Also explain the
      meaning of the pale and dark greys bins.)}}
      % Preferable to rotate the colour table by $180$ deg, to match
      % the colour to the sense of the limits indicated in the
      % bottom-right corner of each plot?
  \label{fig:eso443}
\end{figure*}

>>>>

In general, our Southern Sample galaxies show old, metal-rich and
alpha-enhanced SSPs, characteristics that are common in ETGs {\bf (Add
  a classic reference here.)} The exceptions are NGC~612 and
NGC~1316. NGC~1316 has a very young stellar population (our fit of
$t\approx2$~Gyr is consistent with that of \citealt{Kuntschner2000},
but is conflicting with the older and less metal-rich estimate of
\citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
$\mathrm{[Fe/H]}=0.12\pm0.01$ for an aperture covering the central
$0.1$~kpc). {\bf (Is that a circular or square aperture? If circular,
  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
to have an extended young stellar population of
$t\approx4$~Gyr. Otherwise, NGC~3557 is notable for containing a
significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr)
along the south-east branch of the molecular gas (\removed{white} 
\added{cyan} contours in
Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
  to in the NGC3100 maps, and the CO is distributed North-East to
  South-West, so there is no South-East CO ``branch''. Perhaps you
  meant South-West (where there is indeed a blue region in the
  H$\beta$ map, if not in the age map)? Also, there is no white
  contour in the figure. The CO contours are in pale
  blue/turquoise. Is that what you meant? In any case, this needs to
  be corrected to reflect the truth.)}

@@

\added{\citet{McDermid2006}} \removed{\citet{Kuntschner2010}} showed that 
KDCs can be separated into two classes: either small with various stellar 
ages or typically larger but containing a homogeneously old stellar 
population. {\bf (I thought the first to point this out was 
McDermid et al.\ (2006; see e.g.\ their Fig.~16), which should at 
least also be quoted here. Check and possibly correct.)} 
\added{Using the method of \ctiet{McDermid2006},} the size 
\added{and age} of the KDC is defined as the radius
where the superposition of the two kinematic components (the KDC and
the host galaxy) results in a local minimum in the mean velocity \added{and} the
age of the most-likely SSP model for the spatially integrated spectrum
within a central \added{, circular} aperture with a \added{radius} of 
$1\arcsec$ {\bf (Again, square or circular, radius or diameter? Clarify.)} 
\removed{is taken as the KDC's age.} \added{, respectively.} 
{\bf (Are these two definitions (of the KDCs' sizes and ages) 
those of \citealt{Kuntschner2010} or yours or both? Clarify.)}

@@

\textbf{NGC~3100} has an interesting ISM morphology. The
\ce{^{12}CO(2-1)} integrated intensity contours (overlaid on the IFS
maps in \removed{white} \added{cyan}; see Fig.~\ref{fig:ngc3100}) 
{\bf (Again, no white
  contours in the figure... pale blue/turquoise contours?)} show a
broken ring, the radio jet passing through the gaps, hence suggesting
a jet-ring interaction \citep[see][]{ruffa2019, ruffa2020}. The
ionised gas is brightest in those same gaps, that we interpret as
additional excitation of the gas due to shocks from the impact of the
jet. It is unclear if the ionised gas kinematics supports this
interpretation, being completely different than that of the stars (and
nearly totally blueshifted). The centre of rotation of the gas also
appears to be offset from the centre of the galaxy (as defined by its
stellar surface brightness), by several arcseconds to the west. {\bf
  (I really do not understand how you can identify a centre of
  rotation when there is no evidence of organised rotation at
  all. Either convince me of that or remove/change that
  comment. Perhaps mention the lack of obvious large-scale rotation
  instead?!)}

@@

To check if the LINER classifications are due to central radiation
sources (such as AGN) or extended sources (such as weak star formation
or stars on the post-asymptotic giant branch, pAGB), {\bf (What about
  extended horizontal branch stars (again below)? Mention/discuss.)}
we examine the H$\alpha$ and H$\beta$ flux radial profiles of our
Southern Sample galaxies with extended detected ionised gas (see
Section~\ref{subsubsec:Hb}). Finally, we use the mass\,--\,excitation
(MEx) plot of \cite{Nyland2016}, using parameters derived from \added{a} 
spectra \added{produced by} spatially-\removed{integrated}\added{integrating} over \added{a} central circular apertures of radius
$3\arcsec$ \added{to probe} \removed{, thus probing only} the central 
regions of the galaxies (see
Section~\ref{subsubsec:MEx}). {\bf (You talked here of *the*
  spatially-integrated spectra, as if spectra within a central
  $3\arcsec$ aperture had been used before, but this is not the case
  (only $2\arcsec$ and $1\arcsec$ apertures were used for stellar
  populations). Are these new or previously-generated spectra?
  Clarify.)} This allows us to classify the remaining galaxies (with
no spatially-extended ionised gas) into the star-forming, Seyfert~2,
LINER, transition or passive class, and to subdivide LINER galaxies
into those whose LINER characteristics are attributable to a central
AGN (labelled as LINER-AGN) and those whose LINER characteristics are
not \added{(simply labelled as LINER: they may be AGN or LIER)}. 
{\bf (Labelled as what? LIER?  Clarify.)} As the least
conventional, we expand on the final two steps in the two sub-sections
below, while the final classifications are listed in~Table
\ref{tab:derivedProp}.

@@

In Section~\ref{sec:StarKine}, we showed that in terms of their
stellar kinematic properties our radio-selected Southern Sample
galaxies are no different than ordinary optically-selected ETGs, i.e.\
our sample shows a mixture of regularly- and non-regularly-rotating
objects. \removed{Both classes also appear consistent with observations of the
intrinsic shapes of ordinary regular and non-regular rotators.} {\bf (I
  do not actually know/understand what you were trying to say or refer
  to in the last sentence. Are you referring to the misalignment angle
  $\Gamma_\text{kin}$ of regular and non-regular rotators? What do you
  mean by ``observations of the intrinsic shapes''? Clarify.)} We
established that two (tentatively three) galaxies host a large KDC. We
also classified our sample galaxies into fast- and slow-rotators and,
once differences in the mass distributions of our Southern Sample and
the A+M sample were taken into account, we found a fraction of
slow-rotators ($45\pm13\%$) consistent with that of ordinary ETGs.

@@

In Section~\ref{sec:gas}, we showed that our Southern Sample galaxies
have ionised gas masses of $10^4$\,--\,$10^6$~$\mathrm{M_\odot}$. As
our sample contains particularly massive galaxies, high ionised gas
masses are not unexpected, but these masses are at the upper limit of,
and \removed{possibly} \added{occasionally} exceed {\bf (Again, why ``possibly''? They either always
  exceed, generally exceed, occasionally exceed, or never exceed!
  Check and clarify.)}, the typical masses observed in ETGs,

@@

JW acknowledges funding from the Science and Technology Facilities
Council Grant Code 1577871. This research made extensive use of
observation from VIMOS \citep{LeFevre2003} and archival data from MUSE
\citep{Bacon2010}. We also made use of observations from APEX
\citep{Gusten2006} and ALMA. ALMA is a partnership of ESO
(representing its member states), the National Science Foundation
(NSF; USA) and the National Institutes of Natural Sciences (NINS;
Japan), together with the National Research Council (NRC; Canada), the
Ministry of Science and Technology (MOST; Taiwan) and Academia Sinica
Institute of Astronomy and Astrophysics (ASIAA; Taiwan), and Korea
Astronomy and Space Science Institute (KASI; Republic of Korea), in
cooperation with the Republic of Chile. The Joint ALMA Observatory is
operated by ESO, Associated Universities Inc./National Radio Astronomy
Observatory (AUI/NRAO; USA) and National Astronomical Observatory of
Japan (NAOJ). We also made use of data products from 2MASS, which is a
joint project of the University of Massachusetts and the Infrared
Processing and Analysis Center (IPAC)/California Institute of
Technology, funded by the National Aeronautics and Space
Administration (NASA) and NSF. We also made use of the Set of
Identifications, Measurements and Bibliography for astronomical Data
(SIMBAD) database and portal tool, operated at the Strasbourg
astronomical Data Centre (CDS), France. This research has made use of
the following resources and programs: arXiv.org; the Astrophysics Data
System (ADS); \textsc{astropy}, a community-developed core
\textsc{python} package for astronomy
\citep{TheAstropyCollaboration2013}; \textsc{kinemetry}
\citep{Krajnovic2006}; \textsc{ipython} \citep{Perez2007};
\textsc{matplotlib} \citep{Hunter2007}; \textsc{p3d}
\citep{Sandin2010, Sandin2011}; \textsc{pPXF} \citep{Cappellari2004};
\textsc{py3d} \citep{Sanchez2011, Husemann2013, Husemann2014};
\textsc{scipy} \citep{Oliphant2007, Millman2011}; \textsc{numpy}
\citep{VanderWalt2011}; \textsc{spectools} (Ryan Houghton and Simon
Zieleniewski, private comm.); and \textsc{voronoi\_2d\_binning}
\citep[including the SAURON \added{Colourmaps}\removed{colourmaps} 
{\bf (Colourmaps, whatever that might be, or colour table? Clarify.)}; ][]{Cappellari2003}.

@@

\begin{figure*}
  \centering
  % \includegraphics[width=\textwidth]{eso443-g024.png}
  \caption{Spatially-resolved map of all the parameters derived from
    the VIMOS observations of ESO~443-G24. Each parameter is indicated
    in the top-left corner of each panel, and the colour scale limits
    are listed in the bottom-right corner of each panel. {\bf (Why are
      these not perfect fits to the bottom-right corners? Fix?)} The
    surface brightness (isophotes) are overlaid as black contours in
    all the maps, while the \ce{^{12}CO(2-1)} contours from ALMA are
    overlaid in \removed{white} \added{cyan} {\bf (Pale blue or 
    turquoise? Correct.)} and the
    radio continuum contours from the VLA are overlaid in green. The
    radio band displayed depends on the data and angular resolution
    available \citep[see][]{ruffa2019, ruffa2020}. {\bf
      (``Metalicity'' should be ``Metallicity''. Also explain the
      meaning of the pale and dark greys bins.)}}
      % Preferable to rotate the colour table by $180$ deg, to match
      % the colour to the sense of the limits indicated in the
      % bottom-right corner of each plot?
  \label{fig:eso443}
\end{figure*}
